%-------------------------
% Resume in Latex
% Author : Igor Loskutov
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://www.loskutoff.com/}{\Large Igor Loskutov | Full Stack Developer}} & Email : \href{mailto:igor@loskutoff.com}{igor@loskutoff.com}\\
  \href{http://www.loskutoff.com/}{http://www.loskutoff.com} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Monadical}{Quebec, CA, Remote}
        {Full Stack}{2022 - Now}
        \resumeItemListStart
            \resumeItem{Graph-based funds distribution system}
                {Wrote an event-driven temporal deterministic system for running funds and content distribution algorithms}
            \resumeItem{Double-entry accounting system}
                {Wrote a double-entry accounting system over PostgreSQL to track unconventional flow of debits/credits. Stripe/Paypal integrations.}
            \resumeItem{Double-entry accounting system}
                {Improved developer experience of the team by setting up a CI/CD pipeline with Kubernetes and Github Actions, and by introducing a monorepo project structure}
        \resumeItemListEnd

    \resumeSubheading
      {DesignerAdvantage}{Newton, MA, US, Remote}
      {Frontend Developer}{2021 - 2022}
      \resumeItemListStart
        \resumeItem{CRM for interior design project companies frontend}
          {Helped the client secure funding round by speeding up development. Left codebase well maintainable and easy to build upon. Supervised and guided staff engineers. Although the project being a simple CRUD, challenges were tight time span to deliver and artificial API restrictions (Salesforce)}
      \resumeItemListEnd

    \resumeSubheading
      {FiddleQuest LLC}{Rogue River, OR, US, Remote}
      {Lead Developer}{Dec 2014 - Present (retainer)}
      \resumeItemListStart
        \resumeItem{Violin teaching/learning app. React/Node.js/Meteor.js App (Typescript)}
          {The product I’ve made from scratch and evolved over the years, took the business to a new level. It’s currently an integral part of their education process. Featuring realtime DB → UI updates done in performant and maintainable way. Billing with Stripe, subscription/discounts/coupon system, properly synchronized two-way with Webhooks}
        \resumeItem{React Native iOS/Android apps}
          {Cross-platform work with camera, video pre-encoding, secure upload to AWS S3, post-handling with AWS Transcoder}
        \resumeItem{HTML5 Game}
          {Core logic scripting, inventory / badges (achievements) / "points" for uploaded through the mobile app videos. Typescript, React.js, AWS (SQS, DynamoDB, Lambda, SNS), Docker}
      \resumeItemListEnd

    \resumeSubheading
      {TheHireStreet}{London, UK, Remote}
      {Software Engineer}{Dec 2016 - Apr 2021}
      \resumeItemListStart
        \resumeItem{Java/Lombok (Dropwizard), Typescript (React)}
          {Rental system for catering businesses and individuals. Modernized the current Java/jQuery product (to React)}
      \resumeItemListEnd

    \resumeSubheading
      {An Ethereum based Crypto DEX. Mostly NDA}{Remote}
      {Software Engineer}{Dec 2016 - Apr 2021}
      \resumeItemListStart
        \resumeItem{Frontend, React (JS), Redux}
          {Integrated Metamask and hardware wallets with their Ethereum contract. Charts}
      \resumeItemListEnd

    \resumeSubheading
      {Danke Games}{Heidelberg, Germany, Remote}
      {Software Engineer}{Sep 2013 - Nov 2014}
      \resumeItemListStart
        \resumeItem{Yarnee, Instagram stories before they were a thing. Angular, DevOps}
          {Frontend (AngularJS), Backend (Python/Pyramid). I also have made the app horisontally scalable with the AWS stack}
      \resumeItemListEnd

    \resumeSubheading
      {Megaplan}{Moscow, Russia}
      {Software Engineer}{May 2012 - Feb 2013}
      \resumeItemListStart
        \resumeItem{Helpdesk development, Java/Scala}
          {I wrote them a helpdesk system integrated with development task management using Atlassian JIRA plugin system}
        \resumeItem{Custom Postgres Failover solution (Scala, Apache Zookeeper)}
          {Before Postgres had it as a feature}
      \resumeItemListEnd




%    \resumeSubheading
%      {Intelligence and Innovations}{Moscow, Russia}
%      {Software Engineer}{Dec 2010 - Jun 2011}
%      \resumeItemListStart
%        \resumeItem{Company website development and maintenance}
%          {PHP, Drupal, even ActionScript/Flash (a mall map that works with REST API.)}
%      \resumeItemListEnd



      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Backend}{: TypeScript, Java, Scala, Rust, Rails. SQL, ORMs}
      \hfill
    }
    \item{
      \textbf{Frontend and mobile}{: Typescript, React (+Native), Redux, GraphQL, WebAssembly}
      \hfill
    }
    \item{
      \textbf{Infra}{: AWS, CloudFlare, DigitalOcean, Ansible, Terraform, Kubernetes, GitHub Actions, Heroku. Document databases, Neo4j, Redis, Kafka, RabbitMQ, Elastic}
      \hfill
    }
    \item{
      \textbf{Misc}{: TDD, DDD, System Analysis, Functional Programming, Haskell, Clojure}
    }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Moscow Technological University \& Toljatti Technical University}{Moscow \& Toljatti, Russia}
      {Bachelor of Engineering in Computer Science}{2012 - 2016}
  \resumeSubHeadingListEnd

%-----------Certs-----------------
  \section{Certs}
    \resumeSubHeadingListStart
      \item
        {Oracle Certified Expert, Java EE Enterprise JavaBeans Developer}
      \item
        {Oracle Certified Professional, Java SE Programmer}
      \item
        {Zend Certified Engineer PHP}
      \item
        \href{https://cert.tough-dev.school/eS8vL3fj6ZMuKuBvqcpKQS/en}{System Analysis by tought-dev.school}
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
